Contextuality and Nonlocality in Discrete Quantum Theory

### 2015-11-24 DQC3.tex
Fix a typo in the title page...
Adding comments since "The Concept of Contextuality and its Role in ..."

\author{John Gardiner$^{1}$, Andrew J. Hanson$^{2}$, Gerardo Ortiz$^{3}$,
Amr Sabry$^{1}$, Yu-Tsung Tai$^{42}$}

@@

@@

>>>>

\author{John Gardiner$^{1}$, Andrew J. Hanson$^{2}$, Gerardo Ortiz$^{3}$,
Amr Sabry$^{2}$, Yu-Tsung Tai$^{4,2}$}

@@

\yutsung{Does the sentences in this paragraph contradict to each
other? I think Peres~\cite{peres1995quantum} means: If we think
the measurement process as a quantum system by the Born rule, the
measurement result does not depend on simultaneously measuring commuting
observables. On the other hand, if we want to think the measurement
process classically, i.e., to assign the measurement result for each
observable, we cannot make the assignment prior to any measurement,
and assume that measuring commuting observables does not change the
assigned measurement result. <- This long sentence means contextuality.}

@@

\yutsung{I don't understand the last sentence...}
